### 2024-02-17 paper_sisc_first_revision/localpsf.tex
addressing issues raised by Nicole

It is acceptable if the support of $\impulseresponse_x$ is not perfectly contained in a localized region (violating Assumption 2), so long as the bulk of the ``mass'' of $\impulseresponse_x$ is contained in a localized region. In this case the method can still be applied, but the ellipsoid impulse response support estimates will be large. Therefore, only a small number of impulse responses can be computed per batch. This means that more batches, and hence more operator applies, are needed to form an accurate approximation.

@@

If there are negative numbers in the integral kernel (violating Assumption 3), the ellipsoid estimation procedure may incur errors or fail, leading to poor performance or failure of the PSF method. In Figure \ref{fig:robustness_to_negatives} we investigate the robustness of the ellipsoid support estimation procedure to violations of Assumption 3. We study two integral kernel examples, both of which are parameterized by a quantity that controls how negative the kernels are. We make the following observations:
\begin{itemize}
	\item The larger and more numerous the negative numbers are, the more inaccurate the ellipsoid support estimate is.
	\item The further away from the center of the ellipsoid the negative numbers are, the more influence they have on the quality of the ellipsoid support estimate. This is because moment formulas (Equations \ref{eq:define_mean} and \ref{eq:define_cov}) assign more weight to entries in the kernel that are further from the center.
	\item Negative numbers in the integral kernel affect the method more if they are isolated, and less if they are balanced by nearby positive numbers.
	\item As kernels become more negative, the ellipsoid estimation performs well up to a certain threshold that depends on the spatial distribution of negative and positive entries. After that threshold is crossed, the estimation rapidly transitions to performing poorly and ultimately failing.
\end{itemize} 
%The location of the negative numbers also affects the accuracy of the ellipsoid estimates substantially, but in a more complicated manner. 
For the kernel in the left two columns of Figure \ref{fig:robustness_to_negatives}, negative numbers are interspersed with positive numbers, allowing us to include a large amount of negative numbers in the integral kernel before the method fails. For the kernel in the right two columns, the ellipsoid estimate fails with tiny amounts of negative numbers because the negative numbers are far away from the mean and not balanced by positive numbers at similar distances and angles. In the bottom two rows, we see that the method rapidly transitions from performing reasonably well to performing poorly with only a small change to the integral kernel.

@@

\begin{figure}
	\centering
	{
		%	\setlength{\tabcolsep}{0.1em}
		%	\renewcommand{\arraystretch}{2.0}
		\begin{tabular}{cccc}
	\includegraphics[scale=0.3, valign=c]{frog_ellipsoid_a=1.0.png} & 
	\includegraphics[scale=0.3, valign=c]{frog_1d_a=1.0.png} & 
	\includegraphics[scale=0.3, valign=c]{ricker_ellipsoid_a=0.0.png} & 
	\includegraphics[scale=0.3, valign=c]{ricker_1d_a=0.0.png} \\
	%
	\includegraphics[scale=0.3, valign=c]{frog_ellipsoid_a=20.0.png} & 
	\includegraphics[scale=0.3, valign=c]{frog_1d_a=20.0.png} & 
	\includegraphics[scale=0.3, valign=c]{ricker_ellipsoid_a=0.23.png} & 
	\includegraphics[scale=0.3, valign=c]{ricker_1d_a=0.23.png} \\
	%
	\includegraphics[scale=0.3, valign=c]{frog_ellipsoid_a=27.0.png} & 
	\includegraphics[scale=0.3, valign=c]{frog_1d_a=27.0.png} & 
	\includegraphics[scale=0.3, valign=c]{ricker_ellipsoid_a=0.249.png} & 
	\includegraphics[scale=0.3, valign=c]{ricker_1d_a=0.249.png} 
	\end{tabular}
	}
	\caption{Illustration of the influence of negative numbers in the integral kernel on the robustness of the ellipsoid estimates for the supports of impulse responses. Left two columns: spatially variant blurring kernel given in Equation \ref{eq:frog_kernel}. Right two columns: Ricker wavelet-type kernel given by $\Aker(y,x) = (1 - a \theta)\exp\left(-\theta/2\right)$, where $\theta=(y-x)^T \Sigma^{-1} (y-x)$, and $\Sigma=\operatorname{diag}\left(0.0025, 0.01\right)$. Ordered from top to bottom, the results are obtained with $a\in\{1.0, 20.0, 27.0\}$ for the blur kernel, and $a\in \{0.0, 0.23, 0.249\}$ for the Ricker wavelet-type kernel. Columns 1 and 3: impulse responses for the blur and Ricker wavelet-type kernels, respectively, with estimated support ellipsoids indicated by the black ellipses. Red and blue represent positive and negative numbers in the integral kernel, respectively. Columns 2 and 4: one-dimensional slice along the horizontal line indicated in the two-dimensional plots. The dashed gray line is at zero.
	}
	\label{fig:robustness_to_negatives}
\end{figure}

>>>>

It is acceptable if the support of $\impulseresponse_x$ is not perfectly contained in a localized region (violating Assumption 2), so long as the bulk of the ``mass'' of $\impulseresponse_x$ is contained in a localized region. In principle, the method can be applied even if the impulse responses are not localized. However, in this case only a small number of impulse responses can be computed per batch, which means more batches, and hence more operator applies, are needed to form an accurate approximation.

@@

If there are negative numbers in the integral kernel (violating Assumption 3), the ellipsoid estimation procedure may incur errors or fail, leading to poor performance or failure of the method. In Figure \ref{fig:robustness_to_negatives} we investigate the robustness of the ellipsoid support estimation procedure to violations of Assumption 3. We study two integral kernel examples, both of which are parameterized by a quantity that controls how negative the kernels are. We make the following observations:
\begin{itemize}
	\item The larger and more numerous the negative numbers are, the more inaccurate the ellipsoid support estimate is.
	\item The further away from the center of the ellipsoid the negative numbers are, the more influence they have on the quality of the ellipsoid support estimate. This is because moment formulas (Equations \ref{eq:define_mean} and \ref{eq:define_cov}) assign more weight to entries in the kernel that are further from the center.
	\item Negative numbers in the integral kernel affect the method more if they are isolated, and less if they are balanced by nearby positive numbers.
	\item As kernels become more negative, the ellipsoid estimation performs well up to a certain threshold that depends on the spatial distribution of negative and positive entries. After that threshold is crossed, the estimation rapidly transitions to performing poorly and ultimately failing.
\end{itemize} 
%The location of the negative numbers also affects the accuracy of the ellipsoid estimates substantially, but in a more complicated manner. 
For the kernel in the left two columns of Figure \ref{fig:robustness_to_negatives}, negative numbers are interspersed with positive numbers, allowing us to include a large amount of negative numbers in the integral kernel before the method fails. For the kernel in the right two columns, the ellipsoid estimate fails with tiny amounts of negative numbers because the negative numbers are far away from the mean and not balanced by positive numbers at similar distances and angles. In the bottom two rows, we see the aforementioned threshold effect, in which the method rapidly transitions from performing reasonably well to performing poorly with only a small change to the integral kernel.

@@

\begin{figure}
	\centering
	{
		%	\setlength{\tabcolsep}{0.1em}
		%	\renewcommand{\arraystretch}{2.0}
		\begin{tabular}{cccc}
	\includegraphics[scale=0.3, valign=c]{frog_ellipsoid_a=1.0.png} & 
	\includegraphics[scale=0.3, valign=c]{frog_1d_a=1.0.png} & 
	\includegraphics[scale=0.3, valign=c]{ricker_ellipsoid_a=0.0.png} & 
	\includegraphics[scale=0.3, valign=c]{ricker_1d_a=0.0.png} \\
	%
	\includegraphics[scale=0.3, valign=c]{frog_ellipsoid_a=20.0.png} & 
	\includegraphics[scale=0.3, valign=c]{frog_1d_a=20.0.png} & 
	\includegraphics[scale=0.3, valign=c]{ricker_ellipsoid_a=0.23.png} & 
	\includegraphics[scale=0.3, valign=c]{ricker_1d_a=0.23.png} \\
	%
	\includegraphics[scale=0.3, valign=c]{frog_ellipsoid_a=27.0.png} & 
	\includegraphics[scale=0.3, valign=c]{frog_1d_a=27.0.png} & 
	\includegraphics[scale=0.3, valign=c]{ricker_ellipsoid_a=0.249.png} & 
	\includegraphics[scale=0.3, valign=c]{ricker_1d_a=0.249.png} 
	\end{tabular}
	}
	\caption{Illustration of the influence of negative numbers in the integral kernel on the robustness of the ellipsoid estimates for the supports of impulse responses. Left two columns: spatially variant blur kernel given in Equation \ref{eq:frog_kernel}. Right two columns: Ricker wavelet-type kernel given by $\Aker(y,x) = (1 - a \theta)\exp\left(-\theta/2\right)$, where $\theta=(y-x)^T \Sigma^{-1} (y-x)$, and $\Sigma=\operatorname{diag}\left(0.0025, 0.01\right)$. Ordered from top to bottom, the results are obtained with $a\in\{1.0, 20.0, 27.0\}$ for the left two columns, and $a\in \{0.0, 0.23, 0.249\}$ for the right two columns. Columns 1 and 3: impulse responses with estimated support ellipsoids indicated by the black ellipses. Red and blue represent positive and negative numbers in the integral kernel, respectively. Columns 2 and 4: one-dimensional slice along the horizontal line indicated in the two-dimensional plots. The dashed gray line is at zero.
	}
	\label{fig:robustness_to_negatives}
\end{figure}
